Alien species

### 2023-03-15 DRAFT_alien_species.Rmd
minor text edits

Upper reference value is then 1, and lower reference value is 7, on the R7 scale.
For the threshold value I will set this to value 4 on the R7 scale. 
This is based on interpretation of the definition of this value in Fig. \@ref(fig:R7). 
Step 4 on the R7 scale is the step that, concordantly, best matches the 5% threshold in the old approach, as seen from Fig. \@ref(fig:fremmedart-prosentVSinnslag).

@@

We are only interested in a mapping units that include our target variables.

```{r}
myVars <- c('7TK', '7SE', 'PRTK', 'PRSL')
```

```{r}
naturetypes_summary <- naturetypes_summary_import %>%
  rowwise() %>%
  mutate(keepers = sum(c_across(
    myVars)>0, na.rm=T)) %>%
  filter(keepers > 0) %>%
  select(Nature_type, NiN_mainType, Year)
```

This deleted `r nrow(naturetypes_summary_import) - nrow(naturetypes_summary)` nature types and left us with these:

>>>>

Upper reference value is then 1, and lower reference value is 7, on the R7 scale.
For the threshold value I will set this to value 4 on the R7 scale. 
This is based on interpretation by the author and based of the definition of this value in Fig. \@ref(fig:R7). 
Step 4 on the R7 scale is the step that, concordantly, best matches the 5% threshold in the old approach, as seen from Fig. \@ref(fig:fremmedart-prosentVSinnslag).

@@

We are only interested in a mapping units that include our target variables. The variable _fremmedartsinnslag_ is coded as 7FA.

```{r}
myVars <- '7FA'
```

```{r}
naturetypes_summary <- naturetypes_summary_import %>%
  rowwise() %>%
  mutate(keepers = sum(c_across(
    all_of(myVars))>0, na.rm=T)) %>%
  filter(keepers >0) %>%
  select(Nature_type, NiN_mainType, Year)
```

This deleted `r nrow(naturetypes_summary_import) - nrow(naturetypes_summary)` nature types and left us with these `r nrow(naturetypes_summary)` naturetypes where 7FA was recorded:
